%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
    \cventry
      {IC Systems Design Engineer} % Job Title
      {Crypto Quantique Ltd.} % Organisation
      {Nov. 2022 -- Present} % Location
      {London, UK} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Have sole responsibility for the RTL to GDSII flow at Crypto Quantique, having overseen migration of the EDA tool flow through 2 seperate vendor toolchains and for preparing both IP and Testchip deliveries at the block and top hierarchy levels.}
          \item {Have gained significant experience using TCL, BASH and Python in preparing scripted flows for Synopsys Digital EDA tools from scratch.}
          \item {Experienced in every step of the digital implementation flow; from design \& library preparation to synthesis, through place-and-route, STA and finally physical verification.}
          \item {Contributed to 5 seperate IP deliveries and 3 full-chip tapeouts across a range of foundry services providers and process nodes; TSMC40ULP, GF22FDX \& TSMC12FFC among others.}
          \item {Contributed to detailed RTL design at the block-level and additionally at the system level across a range of IP's and functions.}
          \item {Gained experience with RTL simulation and scripting using Siemens Questa \& Synopsys VCS.}
          \item {Worked side-by-side with the analog design team to integrate the different components of multiple mixed-signal designs.}
          \item {Led the developement and architectural discussions to guide the direction of Crypto Quantique's hardware product portfolio.}
          \item {Managed the hiring and training processes for internships at CQ, including providing mentorship and day-to-day supervision of test hardware and platform development.}
          \item {Actively involved in specification definitions for externally contracted work.}
          \item {Developed and is maintaining the environment for CQ design documentation using Python, and providing access to all team-members through an internal CI/CD flow to ensure updates are continually available to users for reference.}
          \item {Was nominated for and won the \textbf{EW Brightsparks Award} at the Elektra Awards 2023.}
        \end{cvitems}
      }

    \cventry
      {IC Test \& Characterisation Engineer} % Job Title
      {} % Organisation
      {Jul. 2021 -- Nov. 2022} % Location
      {} % Date(s)
      {
        \begin{cvitems}
          \item{Responsible for Test Platform Development using LabView \& Python; undertook significant development effort to build the environment from scratch, integrating several benchtop instruments for automated measurement and test, writing a complete scripting interface for other teams members in python and providing additional software support to facilitate block-level testing of internally developed ASICs.}
          \item{Test Hardware Development in Altium Designer \& Xilinx Vivado and Hardware Driver Devlopment in C/C++ \& Python.}
          \item{Begun to develop system integration skills in a mixed signal ASIC environment; designing in Cadence Virtuoso with ADE and running SPICE simulations.}
          \item{Conducted \& automated ultra-low noise measurements in the lab environment for ASIC characterisation; these measurements were in the femtoampere range and required significant time in testbench development to ensure accurate, reliable and repeatable results.}
        \end{cvitems}
      }

  %---------------------------------------------------------
    \cventry
      {Project Technical Assistant (Internship/Placement Year)}
      {Brunel Innovation Centre}
      {Aug 2018 -- Jul 2019}
      {Cambridge, UK}
      {
        \begin{cvitems}
          \item Schematic capture \& mixed-signal PCB design using Altium Designer
          \item Electronic manufacture including purchasing, design verification and prototype testing using industry-standard test equipment
          \item System software development: STM32 firmware \& microcontroller integration
        \end{cvitems}
      }

  %---------------------------------------------------------
    \cventry
      {Production Technician (Lighting \& Video)}
      {Siyan Ltd.}
      {Aug 2019 -- Present}
      {High Wycombe, UK}
      {
        \begin{cvitems}
          \item Taking responsibility as the sole company representative on site, managing small teams of external contractors on-site
          \item Detailed preparation of equipment and logistics
          \item Video Engineering - LED Wall \& Projection Systems
          \item Entertainment Rigging \& other structural engineering responsibilities
          \begin{itemize}
              \item[--] \textit{\color{awesome} Three-day Rigging for the Entertainment Industry} (Total Training, 2017)
              \item[--] \textit{\color{awesome} Work at Height \& Rescue at Height} (Total Training, 2018)
          \end{itemize}
        \end{cvitems}
      }

  %---------------------------------------------------------
    \cventry
      {Production Technician}
      {Freelance}
      {Feb 2017 -- Aug 2019}
      {London, UK}
      {
        \begin{cvitems}
          \item Ensuring safety standards are met by performing electrical testing of appliances and distribution networks
          \begin{itemize}
              \item[--] \textit{\color{awesome} City \& Guilds BS7909 Temporary Electrical Systems} (BECTU, 2018)
          \end{itemize}
          \item RF Coordination within OFCOM regulations
          \item Audio Engineering \& Sound Reinforcement System Design
          \item On-site IT network installation and management
        \end{cvitems}
      }

  %---------------------------------------------------------

  \end{cventries}
